DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-10-03 2015CompleteDerivation/pictures/independentDof.tex
Including figures for d.o.f.
No need to use calculator package

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{calculator}
\begin{document}
	\begin{tikzpicture}[scale=.4]

@@

	% outer rectangle and diagram name
	\draw (-8,-12) rectangle (34,14);
	\node at (13,-8) {\huge Independent d.o.f.};

@@

	% calculate omega from x and y components
	\SQUARE{\xvar}{\xsquared};
	\SQUARE{\yvar}{\ysquared};
	\ADD{\xsquared}{\ysquared}{\sum};	
	\SQUAREROOT{\sum}{\omegalength};

	% calculate the angle that omega creates w.r.t. the horizontal axis
	\DIVIDE{\yvar}{\xvar}{\sol};	
	\ARCTAN{\sol}{\newsol};
	\RADtoDEG{\newsol}{\thetavar};

	% calculate y prime and theta prime from x prime 
	\SQUARE{\omegalength}{\omegasquared};
	\SQUARE{\xprimevar}{\xprimesquared};
	\SUBTRACT{\omegasquared}{\xprimesquared}{\dif};
	\SQUAREROOT{\dif}{\yprimevar};

	\DIVIDE{\yprimevar}{\xprimevar}{\sol};	
	\ARCTAN{\sol}{\newsol};
	\RADtoDEG{\newsol}{\thetaprimevar};

@@

	\filldraw[fill=red,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\thetavar:(0,0)}]  (0,0) rectangle (\omegalength, \omegalength) node[pos=.5, rotate=\thetavar] {\large $\omega$};

	% drawing the complex right triangle  
	\filldraw[black,fill=yellow,opacity=0.5,rotate around={\thetavar:(\dvar,0)}] (\dvar + \omegalength,0) -- (\dvar,0) -- ++(-\thetaprimevar: \xprimevar) -- ++(\phiprimevar:\yprimevar);

@@

	\filldraw[black,fill=yellow,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\thetavar - \thetaprimevar:(\dvar,0)}]  (\dvar + \xprimevar,0) rectangle (\dvar + \xprimevar + \yprimevar, \yprimevar) node[pos=.5, rotate=\thetavar-\thetaprimevar] {\large $d\hat{q}^2\wedge d\hat{p}_2$};

	\filldraw[black,fill=yellow,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\thetavar:(\dvar,0)}]  (\dvar,0) rectangle (\dvar + \omegalength, \omegalength) node[pos=.5, rotate=\thetavar] {\large $\omega$};

>>>>

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{calc}
\begin{document}
	\begin{tikzpicture}[scale=.4]

@@

	% outer rectangle and diagram name
	\draw (-8,-8) rectangle (34,12.5);

@@

	% calculate omega from x and y components
	\newcommand{\omegalength}{sqrt(\xvar*\xvar+\yvar*\yvar)}

	% calculate the angle that omega creates w.r.t. the horizontal axis
	\newcommand{\thetavar}{atan2(\yvar,\xvar)}

	\newcommand{\yprimevar}{sqrt(\omegalength*\omegalength - \xprimevar*\xprimevar)}

	\newcommand{\thetaprimevar}{atan2(\yprimevar,\xprimevar)}

@@

	\filldraw[fill=red,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\thetavar:(0,0)}]  (0,0) rectangle ({\omegalength}, {\omegalength}) node[pos=.5, rotate={\thetavar}] {\large $\omega$};

	% drawing the complex right triangle  
	\filldraw[black,fill=yellow,opacity=0.5,rotate around={\thetavar:(\dvar,0)}] ({\dvar + \omegalength},0) -- ({\dvar},0) -- ++({-\thetaprimevar}: {\xprimevar}) -- ++({\phiprimevar}:{\yprimevar});

@@

	\filldraw[black,fill=yellow,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\thetavar - \thetaprimevar:(\dvar,0)}]  ({\dvar + \xprimevar},0) rectangle ({\dvar + \xprimevar + \yprimevar}, {\yprimevar}) node[pos=.5, rotate={\thetavar-\thetaprimevar}] {\large $d\hat{q}^2\wedge d\hat{p}_2$};

	\filldraw[black,fill=yellow,fill opacity=0.1,draw opacity=.2,text opacity =1,text=black,rotate around={\thetavar:(\dvar,0)}]  (\dvar,0) rectangle ({\dvar + \omegalength}, {\omegalength}) node[pos=.5, rotate=\thetavar] {\large $\omega$};
